### 2025-01-13 dissertation/chapters/02-artificial-neural-networks.tex
💚 For Taylah, Beané & Aleah

\begin{equation}
      x_{i,p}^{'} = \frac{x_{i,p} - \mu_i}{\sigma^2_i}
      \label{eq:standard_score_scaler}
\end{equation}

@@

\index{Glorot uniform sampling}Glorot uniform sampling is a specialisation of \index{random uniform sampling}random uniform sampling, whereby $\omega_{i} = \sqrt{\frac{6}{fanin + fanout}}$ and $fanin$ is the number of input neurons to the weight vector and $fanout$ is the number of output neurons from the weight vector.

>>>>

\begin{equation}
      x_{i,p}^{'} = \frac{x_{i,p} - \mu_i}{\sigma_i}
      \label{eq:standard_score_scaler}
\end{equation}

@@

\index{Glorot uniform sampling}Glorot uniform sampling is a specialisation of \index{random uniform sampling}random uniform sampling, whereby $\omega_{max} = \sqrt{\frac{6}{fanin + fanout}}$ and $fanin$ is the number of input neurons to the weight vector and $fanout$ is the number of output neurons from the weight vector.

### 2025-01-13 dissertation/chapters/05-probability.tex
💚 For Taylah, Beané & Aleah

\begin{equation}
      \label{eq:probability:probability_distributions:beta:mode}
      M[x] = E[x] - 1 = \frac{\alpha - 1}{\alpha + \beta - 1}
\end{equation}

@@

The \index{Dirichlet probability distribution}Dirichlet probability distribution is a family of multivariate continuous probability distributions over some $\boldsymbol{x}$ in $K$ dimensions~\cite{ref:wackerly:2014}. The \index{Dirichlet probability distribution}Dirichlet probability distribution is a multivariate generalization of the \index{Beta probability distribution}Beta probability distribution and is thus sometimes referred to by its alternative name, i.e. the multivariate Beta probability distribution. The \index{Dirichlet probability distribution}Dirichlet probability distribution is parameterised by some vector $\boldsymbol{\alpha} = (\alpha_{1}$,  $\dots, \alpha_{K}), \forall_{k=1}^{K} \alpha_{k} > 0, \alpha_{k} \in \mathbb{R}$. The parameters, $\boldsymbol{\alpha}$, are referred to as the concentration parameters. The \index{Dirichlet probability distribution}Dirichlet probability distribution of order $K \geq 2$ with parameters $\boldsymbol{\alpha}$, denoted $Dir(\boldsymbol{\alpha})$, has a \acs{PDF} given as

@@

The \index{Categorical probability distribution}Categorical probability distribution is a discrete probability distribution over some random variable, $x$, taking on any one of $K$ possible categories~\cite{ref:wackerly:2014}. There is no ordering to these categories and therefore, for simplicity, each category is assigned a numerical representative value such that $k \in \{1, 2, \dots, K\}$. The probabilities for all outcomes is given by the probability vector $\boldsymbol{\theta} = (\theta_{1}, \dots, \theta_{K})$.  This means that the probability $P(x=k)=\theta_{k}$ has support $x \in \{1, \dots, K\}$. The \index{Categorical probability distribution}Categorical probability distribution, denoted $Cat(\boldsymbol{\theta})$, is a generalization of the \index{Bernoulli probability distribution}Bernoulli probability distribution and is sometimes referred to it by its alternative names, i.e. the generalised \index{Bernoulli probability distribution}Bernoulli probability distribution or the Multinoulli probability distribution. In probability theory, the \index{Categorical probability distribution}Categorical probability distribution is often used to explain the outcome of a single experiment with more than two possible outcomes, such as rolling a six-sided die~\cite{ref:wackerly:2014}. The \acs{PMF} of the \index{Categorical probability distribution}Categorical probability distribution is given as

@@

The \index{Multinomial probability distribution}Multinomial probability distribution is a discrete probability distribution over some random variable $\boldsymbol{x} = (x_{1}, \dots\, x_{K})$ that takes on the counts for each occurrence of $K$ possible classes in $N$ independent trials~\cite{ref:wackerly:2014}. The probabilities for all possible outcomes in a single trial is given by the probability vector, $\boldsymbol{\theta} = (\theta_{1}, \dots, \theta_{K})$. The \index{Multinomial probability distribution}Multinomial probability distribution, denoted $Mul(N, K, \boldsymbol{\theta})$, is thus a generalization of the \index{Binomial probability distribution}Binomial probability distribution to $K$ dimensions. Consider the following special cases:

@@

\begin{figure}[htb]
      \centering
      \includegraphics[width=0.6\textwidth]{images/mouse_experiment_outcome.pdf}
      \caption{The experimental outcomes for the mice-population experiments as was taken from~\cite{ref:hackenberger:2019} .}
      \label{fig:probability:bayesian_statistics:mouse_experiment_outcome}
\end{figure}

>>>>

\begin{equation}
      \label{eq:probability:probability_distributions:beta:mode}
      M[x] = E[x] - 1 = \frac{\alpha - 1}{\alpha + \beta - 2}
\end{equation}

@@

The \index{Dirichlet probability distribution}Dirichlet probability distribution is a family of multivariate continuous probability distributions over some $\boldsymbol{x}$ in $K$ dimensions~\cite{ref:wackerly:2014}. The \index{Dirichlet probability distribution}Dirichlet probability distribution is a multivariate generalisation of the \index{Beta probability distribution}Beta probability distribution and is thus sometimes referred to by its alternative name, i.e. the multivariate Beta probability distribution. The \index{Dirichlet probability distribution}Dirichlet probability distribution is parameterised by some vector $\boldsymbol{\alpha} = (\alpha_{1}$,  $\dots, \alpha_{K}), \forall_{k=1}^{K} \alpha_{k} > 0, \alpha_{k} \in \mathbb{R}$. The parameters, $\boldsymbol{\alpha}$, are referred to as the concentration parameters. The \index{Dirichlet probability distribution}Dirichlet probability distribution of order $K \geq 2$ with parameters $\boldsymbol{\alpha}$, denoted $Dir(\boldsymbol{\alpha})$, has a \acs{PDF} given as

@@

The \index{Categorical probability distribution}Categorical probability distribution is a discrete probability distribution over some random variable, $x$, taking on any one of $K$ possible categories~\cite{ref:wackerly:2014}. There is no ordering to these categories and therefore, for simplicity, each category is assigned a numerical representative value such that $k \in \{1, 2, \dots, K\}$. The probabilities for all outcomes is given by the probability vector $\boldsymbol{\theta} = (\theta_{1}, \dots, \theta_{K})$.  This means that the probability $P(x=k)=\theta_{k}$ has support $x \in \{1, \dots, K\}$. The \index{Categorical probability distribution}Categorical probability distribution, denoted $Cat(\boldsymbol{\theta})$, is a generalisation of the \index{Bernoulli probability distribution}Bernoulli probability distribution and is sometimes referred to it by its alternative names, i.e. the generalised \index{Bernoulli probability distribution}Bernoulli probability distribution or the Multinoulli probability distribution. In probability theory, the \index{Categorical probability distribution}Categorical probability distribution is often used to explain the outcome of a single experiment with more than two possible outcomes, such as rolling a six-sided die~\cite{ref:wackerly:2014}. The \acs{PMF} of the \index{Categorical probability distribution}Categorical probability distribution is given as

@@

The \index{Multinomial probability distribution}Multinomial probability distribution is a discrete probability distribution over some random variable $\boldsymbol{x} = (x_{1}, \dots\, x_{K})$ that takes on the counts for each occurrence of $K$ possible classes in $N$ independent trials~\cite{ref:wackerly:2014}. The probabilities for all possible outcomes in a single trial is given by the probability vector, $\boldsymbol{\theta} = (\theta_{1}, \dots, \theta_{K})$. The \index{Multinomial probability distribution}Multinomial probability distribution, denoted $Mul(N, K, \boldsymbol{\theta})$, is thus a generalisation of the \index{Binomial probability distribution}Binomial probability distribution to $K$ dimensions. Consider the following special cases:

@@

\begin{figure}[htb]
      \centering
      \includegraphics[width=0.6\textwidth]{images/mouse_experiment_outcome.pdf}
      \caption{The experimental outcomes for the mice-population experiments as were taken from~\cite{ref:hackenberger:2019} .}
      \label{fig:probability:bayesian_statistics:mouse_experiment_outcome}
\end{figure}

### 2025-01-13 dissertation/chapters/07-methodology.tex
🍱 (images): Recovered
💚 Dedicated to Taylah, Beané & Aleah
💚 For Taylah, Beané & Aleah

Details around each of these elements are provided in the following sections.

@@

This section provides the details of the low-level \index{heuristic}heuristics that are used in the empirical process. Each of these low-level \index{heuristic}heuristics are implemented as standalone \index{heuristic}heuristics and are also included in the \index{heuristic pool}heuristic pool of the \acs{BHH}. Table \ref{tab:methodology:heuristics} contains a list of all the standalone, low-level \index{heuristic}heuristics that are used as well as their hyper-parameter configurations.

@@

\begin{figure}[htbp]
      \centering
      \includegraphics[width=0.95\textwidth]{images/bhh_heuristic_proxies.pdf}
      \caption{Mapping of proxied heuristic state update operations as implemented by the \acs{BHH}}
      \label{fig:methodology:heuristics:proxies}%
\end{figure}

@@

This section presents the experimental groups that are executed in the empirical process. Three main experimental groups are formulated. Each of these are discussed in more detail in the following sections.

@@

For the standalone \index{heuristic}heuristics experimental group, the \index{heuristic}heuristics, as presented in Section \ref{sec:methodology:heuristics}, are used along with their specified hyper-parameters. Each of these standalone low-level \index{heuristic}heuristics are compared to that of the \acs{BHH} baseline configuration, across all datasets.

@@

Various experimental groups and configurations have been presented in Sections \ref{sec:methodology:experiments:case_study}, \ref{sec:methodology:experiments:standalone_optimisers} and \ref{sec:methodology:experiments:bhh_variants}. The results from each of these experimental groups are statistically analysed. To ensure that there are sufficient samples for statistical analysis, each experiment and configuration is trained for 30 epochs and is repeated over 30 runs, for each of the fourteen datasets. The experimental results contain performance evaluation data for the training and testing datasets, and includes loss and accuracy measurements. Statistical analysis is executed on the results from the testing datasets. An average rank is calculated across all 30 runs, for all experimental groups and configurations, at each step, for every epoch of training. Each run is executed using a unique random seed, such that each run is identical in its setup and configuration, but unique between runs.

>>>>

Details around each of these elements is provided in the following sections.

@@

This section provides the details of the low-level \index{heuristic}heuristics that are used in the empirical process. Each of these low-level \index{heuristic}heuristics is implemented as standalone \index{heuristic}heuristics and is also included in the \index{heuristic pool}heuristic pool of the \acs{BHH}. Table \ref{tab:methodology:heuristics} contains a list of all the standalone, low-level \index{heuristic}heuristics that are used as well as their hyper-parameter configurations.

@@

\begin{figure}[htbp]
      \centering
      \includegraphics[width=0.7\textwidth]{images/bhh_heuristic_proxies.pdf}
      \caption{Mapping of proxied heuristic state update operations as implemented by the \acs{BHH}}
      \label{fig:methodology:heuristics:proxies}%
\end{figure}

@@

This section presents the experimental groups that are executed in the empirical process. Three main experimental groups are formulated. Each of these is discussed in more detail in the following sections.

@@

For the standalone \index{heuristic}heuristics experimental group, the \index{heuristic}heuristics, as presented in Section \ref{sec:methodology:heuristics}, are used along with their specified hyper-parameters. Each of these standalone low-level \index{heuristic}heuristics is compared to that of the \acs{BHH} baseline configuration, across all datasets.

@@

Various experimental groups and configurations have been presented in Sections \ref{sec:methodology:experiments:case_study}, \ref{sec:methodology:experiments:standalone_optimisers} and \ref{sec:methodology:experiments:bhh_variants}. The results from each of these experimental groups is statistically analysed. To ensure that there are sufficient samples for statistical analysis, each experiment and configuration is trained for 30 epochs and is repeated over 30 runs, for each of the fourteen datasets. The experimental results contain performance evaluation data for the training and testing datasets, and includes loss and accuracy measurements. Statistical analysis is executed on the results from the testing datasets. An average rank is calculated across all 30 runs, for all experimental groups and configurations, at each step, for every epoch of training. Each run is executed using a unique random seed, such that each run is identical in its setup and configuration, but unique between runs.

### 2025-01-13 dissertation/preamble/acknowledgements.tex
✨ (dissertation): Chapter 1 done
✨ (final-review): Done up till chapter 1
💚 For Taylah, Beané & Aleah

\begin{quotation}
    \noindent
    ``I've made the most important discovery of my life. It's only in
    the mysterious equation of love that any logical reasons can be found. I'm
    only here tonight because of you. You are the only reason I am \ldots you are
    all my reasons.''
\end{quotation}
\begin{flushright}
    Prof. J.F. Nash, Jr.
\end{flushright}

@@

    \item To my supervisors, Dr. A. Bosman, Prof. C.W. Cleghorn and Prof. A.P. Engelbrecht. Thank you for not giving up on me.

@@

\begin{center}
    This project was made possible by the National Research Foundation (NRF) and the Center for High Performance Computing (CHPC) Cluster at the Council for Scientific and Industrial Research (CSIR).
\end{center}

>>>>

\begin{quotation}
    \noindent ``I've made the most important discovery of my life. It's only in
    the mysterious equation of love that any logical reasons can be found. I'm
    only here tonight because of you. You are the only reason I am \ldots you are
    all my reasons.''
\end{quotation}
\begin{flushright}
    - Prof. J.F. Nash, Jr.
\end{flushright}

@@

    \item To my supervisors, Dr. A.S. Bosman, Prof. C.W. Cleghorn and Prof. A.P. Engelbrecht. Thank you for not giving up on me.

    \item To EPI-USE. Thank you for helping out where I needed it.

@@

\begin{center}
    This project was made possible by the National Research Foundation (NRF) and the Centre for High Performance Computing (CHPC) Cluster at the Council for Scientific and Industrial Research (CSIR).
\end{center}

### 2025-01-13 dissertation/preamble/supervisors.tex
📝 (review): First set of changes
✨ (feat): Review, analysis script updated
✨ (dissertation): Chapter 1 done
💚 For Taylah, Beané & Aleah

\pagestyle{empty}
\vspace*{\fill}
\noindent
\parbox{4cm}{\textbf{Supervisor:}} Dr. A. Bosman \\*[2mm]
\parbox{4cm}{\textbf{~}} University of the Pretoria \\*[2mm]
\parbox{4cm}{\textbf{~}} Department of Computer Science\\*[1cm]
\parbox{4cm}{\textbf{Co-Supervisor:}} Dr. C.W. Cleghorn \\*[2mm]
\parbox{4cm}{\textbf{~}} University of the Witwatersrand\\*[2mm]
\parbox{4cm}{\textbf{~}} Department of Computer Science\\*[1cm]
\parbox{4cm}{\textbf{Co-Supervisor:}} Prof. A.P. Engelbrecht \\*[2mm]
\parbox{4cm}{\textbf{~}} University of Stellenbosch\\*[2mm]
\parbox{4cm}{\textbf{~}} Department of Industrial Engineering\\*[1cm]
\parbox{4cm}{\textbf{Degree:}} Master of Science, Computer Science (Artificial
Intelligence)
\newpage

>>>>

\pagestyle{empty}
\vspace*{\fill}
\noindent
\parbox{4cm}{\textbf{Supervisor:}}\parbox{12cm}{Dr. A.S. Bosman}\\*[2mm]
\parbox{4cm}{\textbf{~}}\parbox{12cm}{University of the Pretoria}\\*[2mm]
\parbox{4cm}{\textbf{~}}\parbox{12cm}{Department of Computer Science}\\*[1cm]
\parbox{4cm}{\textbf{Supervisor:}}\parbox{12cm}{Prof. C.W. Cleghorn}\\*[2mm]
\parbox{4cm}{\textbf{~}}\parbox{12cm}{University of the Witwatersrand}\\*[2mm]
\parbox{4cm}{\textbf{~}}\parbox{12cm}{Department of Computer Science}\\*[1cm]
\parbox{4cm}{\textbf{Supervisor:}}\parbox{12cm}{Prof. A.P. Engelbrecht}\\*[2mm]
\parbox{4cm}{\textbf{~}}\parbox{12cm}{Stellenbosch University}\\*[2mm]
\parbox{4cm}{\textbf{~}}\parbox{12cm}{Department of Industrial Engineering, Computer Science Division}\\*[1cm]
\parbox{4cm}{\textbf{Degree:}}\parbox{12cm}{Master of Science, Computer Science (Artificial Intelligence)}
\newpage
